Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/paper.tex
smaller gridsteps
naive breadth first timings

                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)

@@

                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)

@@

                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)

@@

                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)

@@

                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)

@@

@@

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            Normals & Cubes & Smooth \\
            \hline
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon, then on an
        octaflower as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=3$, while
        our normal estimator are computed using a deviation of $\sigma=3$, and so
        a radius of $r=2\sigma=6$}
        \label{fig:normals-estimation}
    \end{figure}

>>>>

                    (0.0625,7.61948)(0.125,5.49755)(0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)

@@

                    (0.0625,38.1045)(0.125,26.8765)(0.25,19.6747)(0.375,16.6192)(0.5,14.0867)(0.625,12.5062)(0.75,11.3734)(0.875,10.2845)(1,8.90781)

@@

                    (0.0625,25.5024)(0.125,18.2364)(0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)

@@

                    (0.0625,27.9287)(0.125,17.5104)(0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)

@@

                    (0.0625,41.9816)(0.125,27.7104)(0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)

@@

                    orange,
                    mark=square,
                    % torus
                    10624 7172.49\\
                    4968 2330.69\\
                    2584 883.559\\
                    1840 568.776\\
                    1176 278.712\\
                    912 212.285\\
                    624 122.615\\
                    % rcube
                    28568 20358.9\\
                    12632 5964.1\\
                    7088 2631.15\\
                    4664 1394.49\\
                    3080 742.638\\
                    2408 554.389\\
                    1736 334.654\\
                    % sphere9
                    24320 21263.4\\
                    10760 6225.27\\
                    6056 2829.2\\
                    3944 1494.98\\
                    2648 833.047\\
                    2000 579.561\\
                    1520 394.169\\
                    % leopold
                    8336 6866.82\\
                    3720 2232.34\\
                    2104 1050.28\\
                    1336 576.853\\
                    928 354.691\\
                    680 243.249\\
                    520 174.452\\
                    % goursat
                    37592 26954.6\\
                    16712 8358.2\\
                    9512 3748.3\\
                    6056 1921.43\\
                    4088 1088.38\\
                    3032 706.378\\
                    2456 531.932\\
                    % d20
                    97844 26392.3\\
                    390235 110416.0\\
                \addlegendentry{naive breadth first};

@@

    \begin{figure}
        \centering
        \begin{tabular}{|c||c|c|}
            \hline
            Normals & Cubes & Smooth \\
            \hline
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/chinese-dragon-normal-estimation-smooth-NV} \\
            \hline
            \raisebox{18mm}{II} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-II} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-II} \\
            \hline
            \raisebox{18mm}{Ours} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-cubes-NV} &
            \includegraphics[width=0.4\textwidth]{pictures/octaflower-normal-estimation-smooth-NV} \\
            \hline
        \end{tabular}
        \caption{Examples of normals computed on a chinese dragon, then on an
        octaflower as a color map. First set displays II normals, second set
        uses the visibility algorithm to compute them. The normals are colored
        according to their orientation as $0.5 \cdot (n_i + \mathbbm{1})$. The
        right images are the smooth version of the left images. ``Integral
        Invariant normals'' are computed using a radius of $r=4.5$, while
        our normal estimator are computed using a deviation of $\sigma=4$, and so
        a radius of $r=2\sigma=8$}
        \label{fig:normals-estimation}
    \end{figure}
